Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)

### 2020-05-21 doc/paper.tex
Polish the conclusion in the FASE-GLoBES project.

\section{Summary and conclusions}
\textcolor{red}{[JT: This section has to be significantly improved.]}

We have presented a simulation toolkit \textbf{FaSE-GLoBES} to study the leptonic flavour symmetry models with neutrino oscillation experiments in a user-friendly way. \textbf{FaSE} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}. While \textbf{FASE\_GLoBES.c} plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES}, all inputs from the user needs to be given in \textbf{model-input.c}. Two main functions provided by \textbf{FaSE} for users are a convenient way to assign a flavour symmetry model and to include Gaussian priors that can be in oscillation or model parameters.
%
With \textbf{FaSE-GLoBES}, users are able to study how a flavour model can be studied by the simulated experimental configuration in varieties of perspectives, \textit{e.g.} model parameter constraints, hypothesis testing.

{\color{blue}With the progression of the precision measurements in the neutrino physics, and considering the success of the flavour symmetry theory in explaining neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics. Finally, we leave the flexibility for the user, and some other improvements and extensions can be expected in the future.}

>>>>

\section{Summary and conclusions}

With the progress of precision measurements in the neutrino experiments, and the success of numerous flavour symmetry theories to explain tiny neutrino masses, there are strong motivations to test and discriminate theoretical models by the next-generation neutrino oscillation experiments. We have presented a simulation toolkit \textbf{FaSE-GLoBES} to study the leptonic flavour symmetry models with neutrino oscillation experiments in a user-friendly way. \textbf{FaSE-GLoBES} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}. While \textbf{FASE\_GLoBES.c} works as a bridge between models and standard neutrino mixings, all inputs from the user need to be given in \textbf{model-input.c}. With the help of two main functions provided by \textbf{FaSE}, it is convenient to assign a flavour symmetry model and include Gaussian priors associated with oscillation or model parameters. Users are able to study how a flavour model can be studied by the simulated experimental configuration in various perspectives, \textit{e.g.} model parameter constraints, hypothesis testing. {\color{blue} \textbf{FaSE-GLoBES} will contribute to the selection and screening of underlying neutrino mass models by oscillation experiments. Further improvements and extensions can be envisioned as more requests are made by users.}
